\documentclass[techrep,english]{ipsj}

%\usepackage[dvips]{graphicx}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{adjustbox}

\def\Underline{\setbox0\hbox\bgroup\let\\\endUnderline}
\def\endUnderline{\vphantom{y}\egroup\smash{\underline{\box0}}\\}
\def\|{\verb|}

\setcounter{volume}{25}% vol21=2013
\setcounter{number}{1}
\setcounter{page}{1}

\usepackage[varg]{txfonts}
\makeatletter%
\input{ot1txtt.fd}
\makeatother%

\begin{document}

\title{TITLE TBA}

\author{Erwin Raynald de Haan}{TITECH}[email]
\author{Artur Podobas}{TITECH}[podobas.a.aa@m.titech.ac.hp]
\author{Satoshi Matsuoka}{TITECH}[matsu@is.titech.ac.jp]

\begin{abstract}
TODO
\end{abstract}


\maketitle

\section{Introduction}
Artur helps writing this.

\section{Related Work}
Artur can write this.

\section{A FPGA-based CNN Framework}
\subsection{Field-Programmable Gate-Arrays}
Small intro to FPGAs.

\subsection{(Convolutional) Neural Networks}
Small intro to Neural Networks.

\subsection{FPGA CNN Framework}
Small intro to the framework.
\subsubsection{Design overview}
Overview design + picture.
\subsubsection{Design details}
Gruesome details of the design.
\subsubsection{Design decisions}
Decisions taken while designing. The *why* we did as we did.

\section{Methodology}
\subsection{Experimental Platform}
Compiler, version, flags, fpga boards, host, etc.
\subsection{Network Tested + Data-set}
MNIST, Multilayer Perceptron?
number of runs, batch size, etc.

\section{Results}

\subsection{FPGA Resource Utilization}
Area, DSP, Fmax, etc.

\subsection{Training Performance}
Convergence, performance, accuracy, etc.


\end{document}
